\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-17 related.tex
racetrack
simtester

Carburizer\cite{carburizer} is an effort to make imperfect kernel-level drivers work more reliably in the presence of faulty peripheral devices. They use static analysis to identify variables ``tainted'' by device input and unsafe uses thereof. Carburizer is able to transform such badly-written code to be more robust.
Kernel device drivers are a ripe breeding ground for bugs, because they are frequently written by less careful developers, and the sheer volume of code makes it difficult to rigorously review.
Due to the interrupt-driven nature of many drivers, they are also prone to concurrency bugs, which Carburizer does not address.
In Section~\ref{sec:future-drivers} we discuss the potential applicability of systematic exploration to concurrency bugs in kernel device drivers.

@@

Data race detection is the canonical runtime concurrency verification technique. Tools such as ThreadSanitizer\cite{tsan} track synchronisation operations and happens-before relationships to identify unsafe concurrent memory accesses. Such accesses, called ``data races'', might not necessarily cause incorrect behaviour, but are usually warning indicators of such, and represent bad coding practice in any case.

>>>>

Carburizer\cite{carburizer} is an effort to make imperfect kernel-level drivers work more reliably in the presence of faulty peripheral devices. They use static analysis to identify variables ``tainted'' by device input and unsafe uses thereof. Carburizer is able to transform such badly-written code to be more robust.
Kernel device drivers are a ripe breeding ground for bugs, because they are frequently written by less careful developers, and the sheer volume of code makes it difficult to rigorously review.
Due to the interrupt-driven nature of many drivers, they are also prone to concurrency bugs, which Carburizer does not address.

SimTester\cite{simtester} is another tool for testing kernel device drivers. Like Landslide, SimTester uses Simics as its execution environment, and identifies key decision points during execution at which to inject interrupts. SimTester focuses on races involving device interrupt handling code, whereas Landslide is geared towards non-driver inter-thread races. Additionally, SimTester's testing model involves forcing only one interrupt per test run, which is a lighter-weight approach than systematic exploration.

In Section~\ref{sec:future-drivers} we discuss the potential applicability of systematic exploration to concurrency bugs in kernel device drivers.

@@

Data race detection is the canonical runtime concurrency verification technique. Tools such as ThreadSanitizer\cite{tsan} track synchronisation operations and happens-before relationships to identify unsafe concurrent memory accesses. Such accesses, called ``data races'', might not necessarily cause incorrect behaviour, but are usually warning indicators of such, and represent bad coding practice in any case.
\revision{RaceTrack\cite{racetrack} is another data race detection tool notable for its ability to adaptively adjust its testing granularity after some execution analysis.}
